Titeltext

### 2018-07-26 thesis/paper/paper.tex
Added one-of qualifier value

>>>>

\subsection{One-of qualifier value (Q52712340)}
The one-of qualifier value constraint restricts which values may be used on a qualifier with a given property on a constrained statement.

\begin{table}[H]
\caption{One-of qualifier value constraint (Q52712340)}
\begin{tabularx}{\textwidth}{ ll X}
\hline
Requirement & constrained statement qualifier value \\
\hline
Qualifiers: & \makecell{qualifier property (P2306) -- 1 \\ property of the restricted qualifier\\
qualifier values (P2305) -- 1..* \\ values the qualifiers may take}\\
\hline
Violation & \makecell{constrained statement with a qualifier with the qualifier property and a value unequal to all qualifier values} \\
\hline
Dependency & constrained item and qualifiers with the qualifier property \\
\hline
Rule features & inequality \\
\hline
\end{tabularx}
\end{table}

The constraint can be modelled if the inequality between a value of a qualifier property with all qualifier values is given. The violations could then be found by taking a tripleEDB with the constrained property and a qualifier with the qualifier property on the former statement whose value is unequal to all qualifier values.
